\documentclass[notheorems,14pt,compress]{beamer}

\usepackage{fontspec,xltxtra,xunicode}
% math conf
% math symbols and such should go before unicode-math!
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{unicode-math}

\usetheme{ohnosequences}
\usecolortheme{ohnosequences}
% so that fontspec and unicode-math work
% see https://tex.stackexchange.com/questions/26805/how-to-use-unicode-math-with-beamer-and-lualatex
\usefonttheme{professionalfonts}
\usefonttheme{ohnosequences}
\usepackage{amssymb}

\let\OldHref\href
\renewcommand{\href}[2]{\OldHref[pdfnewwindow]{#1}{{\textbf{#2}}}}

\providecommand{\tightlist}{%
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\usepackage{caption}
\setbeamertemplate{caption}{\insertcaption}
% \captionsetup{labelformat=empty,labelsep=none}
% \setbeamertemplate{caption}[numbered]
% \setbeamertemplate{caption label separator}{:}
% \setbeamercolor{caption name}{fg=normal text.fg}
% \usepackage{amssymb,amsmath}
% \usepackage{ifxetex,ifluatex}
% \usepackage{fixltx2e} % provides \textsubscript
% \usepackage{lmodern}
\newcommand{\euro}{€}

% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
% \IfFileExists{microtype.sty}{\usepackage{microtype}}{}


% allow to break lines more easily on tt text
% http://tex.stackexchange.com/questions/52850/temporarily-increase-the-limit-on-space-size
\let\OldTexttt\texttt
\renewcommand{\texttt}[1]{ \emergencystretch=2em \OldTexttt{#1} }
% maybe?
\setlength{\emergencystretch}{3em}  % prevent overfull lines


% Comment these out if you don't want a slide with just the
% part/section/subsection/subsubsection title:
% \AtBeginPart{
%   \let\insertpartnumber\relax
%   \let\partname\relax
%   \frame{\partpage}
% }
% \AtBeginSection{
%   \let\insertsectionnumber\relax
%   \let\sectionname\relax
%   \frame{\sectionpage}
% }
% \AtBeginSubsection{
%   \let\insertsubsectionnumber\relax
%   \let\subsectionname\relax
%   \frame{\subsectionpage}
% }

% \setlength{\parindent}{0pt}
% \setlength{\parskip}{6pt plus 2pt minus 1pt}
% \setlength{\emergencystretch}{3em}  % prevent overfull lines
\usepackage{polyglossia}
\setmainlanguage{english}
% \setotherlanguages{}

\hypersetup{
  pdfnewwindow,
  colorlinks,
  setpagesize     = false,        % page size defined by xetex
  citecolor       = OldCyan-Dark,
  filecolor       = OldCyan-Dark,
  linkcolor       = OldCyan-Dark,
  urlcolor        = OldCyan-Dark,
  urlbordercolor  = OldCyan-Dark
}


\usepackage[noabbrev,capitalize]{cleveref}
\usepackage{amsthm}
% theorem environments
% does not work here
% see https://tex.stackexchange.com/questions/304024/beamer-with-numbered-theorems-not-working-with-cleveref
% \newcounter{dummy}\numberwithin{dummy}{subsection}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
% \newcommand{\propositionautorefname}{Proposition}
% \crefname{proposition}{Proposition}{Propositions}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}
\theoremstyle{definition}
\newtheorem{Def}{Definition}
\newtheorem{Remark}{Remark}
\newtheorem{Example}{Example}

\let\amsmathcolon\colon
\patchcmd{\amsmathcolon}{:}{\colon}{}{}
  \AtBeginDocument{
    \edef\colon{\mathrel{\Umathcharnum\the\Umathcodenum`:}}
    \begingroup\lccode`~=`:
    \lowercase{\endgroup\let~}\amsmathcolon
    \mathcode`:="8000
  }

% specific tex stuff which doesn't work due to YAML escaping []
\DeclareMathOperator{\im}{Im}
\DeclareMathOperator{\coim}{coim}
\DeclareMathOperator{\coker}{coker}
\DeclareMathOperator{\eq}{eq}
\DeclareMathOperator{\coeq}{coeq}
\DeclareMathOperator{\quot}{quot}
\newcommand{\colim}{\varprojlim}
\newcommand{\Sub}{\mathbf{Sub}}
\newcommand{\cat}[1]{\mathcal{#1}}
\newcommand{\Sup}{\mathbf{Sup}}
\newcommand{\DLat}{\mathbf{DLat}}
\newcommand{\SLat}{\mathbf{SLat}}
\newcommand{\LLat}{\mathbf{LLat}}
\newcommand{\Ab}{\mathbf{Ab}}
\newcommand{\Cat}{\mathbf{Cat}}
\newcommand{\Cart}{\mathbf{Cart}}
\newcommand{\Set}{\mathbf{Set}}
\newcommand{\Rel}{\mathbf{Rel}}
\newcommand{\Setd}{\mathbf{Setd}}
\newcommand{\CRig}{\mathbf{CRig}}
\newcommand{\CRing}{\mathbf{CRing}}
\newcommand{\Mon}{\mathbf{Mon}}
\newcommand{\CMon}{\mathbf{CMon}}
\newcommand{\ICMon}{\mathbf{ICMon}}
\newcommand{\CComon}{\mathbf{CComon}}
\newcommand{\ICComon}{\mathbf{ICComon}}
\newcommand{\Mod}{\mathbf{Mod}}
\newcommand{\Dioid}{\mathbf{Dioid}}
\newcommand{\CSLat}{\mathbf{CSLat}}
\newcommand{\Alg}{\mathbf{Alg}}
\newcommand{\SMonCat}{\mathbf{SMonCat}}
\newcommand{\CQuant}{\mathbf{CQuant}}
\newcommand{\Frm}{\mathbf{Frm}}
\newcommand{\Loc}{\mathbf{Loc}}
\newcommand{\Top}{\mathbf{Top}}
\newcommand{\Eq}{\mathbf{Eq}}
\newcommand{\Ker}{\mathbf{Ker}}
\newcommand{\Quot}{\mathbf{Quot}}


\usepackage{booktabs}
\usepackage[scale=2]{ccicons}

\title{era7 bionformatics}
\subtitle{Aλhambra day}
\author{Eduardo Pareja-Tobes, CTO}
\date{2019-05-06}

\begin{document}
\maketitle


% 
\hypertarget{era7}{%
\section{era7?}\label{era7}}

\begin{frame}{%
\protect\hypertarget{the-company-i}{%
The Company I}}

\begin{itemize}
\tightlist
\item
  Founded in \textbf{2006}. Granada, Cambridge MA
\item
  \emph{Biological} \textbf{data analysis} \emph{Genomics, NGS}
\item
  \emph{Wet lab} too: Sequencing
\item
  \textbf{Team} mix of Biology, IT, Maths backgrounds
\end{itemize}

\end{frame}

\begin{frame}{%
\protect\hypertarget{the-company-ii}{%
The Company II}}

\begin{itemize}
\tightlist
\item
  \textbf{Research} Bioinformatics, Biology
\item
  \textbf{100\% Open Source} \emph{AGPLv3}, \textbf{no} dual licensing
\item
  \textbf{Cloud Computing} \emph{AWS}, running on it since
  \textasciitilde{}2007
\end{itemize}

\end{frame}

\hypertarget{software}{%
\section{Software}\label{software}}

\begin{frame}{%
\protect\hypertarget{data-analysis}{%
Data Analysis}}

\begin{itemize}
\tightlist
\item
  \emph{Algorithm} design and implementation
\item
  Low-level DNA sequence analysis
\item
  AWS deployment
\end{itemize}

\end{frame}

\begin{frame}{%
\protect\hypertarget{graph-databases}{%
Graph Databases}}

\begin{itemize}
\tightlist
\item
  \textbf{Bio4j}: since 2008. Graphs for biological data.
\item
  strongly typed graph query language
\item
  Working on our own graph data engine
\end{itemize}

\end{frame}

\begin{frame}{%
\protect\hypertarget{other}{%
Other}}

\begin{itemize}
\tightlist
\item
  \textbf{Webapps}: Mostly for clients using our services.
\item
  \textbf{Elm} client-side, datavis
\end{itemize}

\end{frame}

\hypertarget{scala}{%
\section{Scala}\label{scala}}

\begin{frame}{%
\protect\hypertarget{use}{%
Use}}

In production since Scala 2.7/2.8 \textasciitilde{}2010. 9 years of
experience. We have used it for basically everything:

\end{frame}

\begin{frame}{%
\protect\hypertarget{use-ii}{%
Use II}}

\begin{itemize}
\tightlist
\item
  Data Analysis low-level code
\item
  Language/eDSL implementation (graph data query languages)
\item
  Generic Libraries (ohnosequences/cosas, ohnosequences/stuff, \ldots{})
\item
  Infrastructure (AWS, mostly EC2, S3, SQS, DynamoDB)
\item
  Web Applications (Play)
\end{itemize}

\end{frame}

\begin{frame}{%
\protect\hypertarget{why}{%
Why}}

Team had been working in Java before; FP obvious given team background.
JVM interop a plus (Graph Databases, good AWS support, etc).

\end{frame}

\begin{frame}{%
\protect\hypertarget{learning-scala}{%
Learning Scala}}

Training people has been really hard.

\begin{itemize}
\tightlist
\item
  \emph{Which} Scala?
\item
  Corner cases everywhere
\item
  No good docs anywhere
\item
  \ldots{}
\end{itemize}

\end{frame}

\begin{frame}{%
\protect\hypertarget{happy}{%
Happy?}}

Not really. Currently using it only as a better Java. No time for going
into much detail though.

\end{frame}

\begin{frame}{%
\protect\hypertarget{performance}{%
Performance}}

\begin{itemize}
\tightlist
\item
  awful collections
\item
  really hard to avoid object creation
\item
  generics and fast: pick one (specialization = more bugs)
\item
  value classes = more bugs, no real value
\item
  \ldots{}
\end{itemize}

\end{frame}

\begin{frame}{%
\protect\hypertarget{as-a-better-java}{%
As a better Java}}

Nicer syntax, but\ldots{} mostly that

\begin{itemize}
\tightlist
\item
  interop actually not that good
\item
  Explosion of features/patterns confusing
\item
  Need to know Java anyway
\item
  Java (minus syntax) really close to Java wrt FP
\end{itemize}

Thinking about moving to Kotlin (web apps, infrastructure) and F\# (data
analysis).

\end{frame}

\begin{frame}{%
\protect\hypertarget{as-an-expressive-language}{%
As an Expressive Language}}

\begin{itemize}
\tightlist
\item
  Bugs everywhere
\item
  Type inference is awful
\item
  fake dependent types: more problems than what they solve
\item
  Scala3/Dotty not looking good (dropping type projections, focus on
  singleton types, \ldots{})
\end{itemize}

Since a year ago doing everything in \textbf{Idris} (compilers for graph
data languages, distributed graph DB, \ldots{})

\end{frame}

\begin{frame}{%
\protect\hypertarget{hiring}{%
Hiring?}}

We’re \emph{always} hiring.

\begin{itemize}
\tightlist
\item
  Languages, qualifications not important
\item
  skills, interest, willingness to learn –critical
\end{itemize}

Thank you!

\end{frame}

\end{document}
